Setting up Data

### 2020-01-06 doc/Effects.Rmd
first try of incorporating batch18, still a few bugs

load(file="C:/Users/alpeterson7/Documents/MLH1repo/data/MLH1/MLH1_data_setup_12.20.19.RData")#fixing bugs, formating
load(file="C:/Users/alpeterson7/Documents/MLH1repo/data/total_SC_30.12.19.RData")#total SC data

@@

```{r SC.hitograms, echo=FALSE, fig.width = 4, fig.height=.1}
#try adjusting the size for thi..

skel.histgram <- ggplot(MLH1.merge.Skel, aes(x=skel_size)) +  geom_histogram(bins=50)
skel.histgram

>>>>

load(file="C:/Users/alpeterson7/Documents/MLH1repo/data/MLH1/MLH1_data_setup_1.5.20.RData")#added batch18

#load(file="C:/Users/alpeterson7/Documents/MLH1repo/data/MLH1/MLH1_data_setup_12.20.19.RData")#fixing bugs, formating
load(file="C:/Users/alpeterson7/Documents/MLH1repo/data/total_SC_30.12.19.RData")#total SC data

@@

```{r SC.hitograms, echo=FALSE, fig.width = 4, fig.height=1}
#try adjusting the size for thi..

skel.histgram <- ggplot(MLH1.merge.Skel, aes(x=skel_size)) +  geom_histogram(bins=50)+ggtitle("width 4, height 1")
skel.histgram
```

```{r more.SC.hist, echo=FALSE}

### 2020-01-06 doc/Main_Report_Results.rmd
first try of incorporating batch18, still a few bugs

load(file="C:/Users/alpeterson7/Documents/MLH1repo/data/MLH1/MLH1_data_setup_12.20.19.RData")#fixing bugs, formating
#load(file="data/MLH1/MLH1_data_setup_12.3.19.RData")#removed exclude mice
#load(file="data/MLH1/MLH1_data_setup_11.12.19.RData")#added batch17
#load(file="data/MLH1/MLH1_data_setup_11.11.19.RData")#deleted DUP image
#load(file="data/MLH1/MLH1_data_setup_9.26.19.RData")#added batch16
#load(file="data/MLH1/MLH1_data_setup_8.29.19.RData") #
#load(file="data/MetaData.RData") #this was replacing most updated data file

>>>>

load(file="C:/Users/alpeterson7/Documents/MLH1repo/data/MLH1/MLH1_data_setup_12.20.19.RData")#batch18
#load(file="C:/Users/alpeterson7/Documents/MLH1repo/data/MLH1/MLH1_data_setup_12.20.19.RData")#fixing bugs, formating
#load(file="data/MLH1/MLH1_data_setup_12.3.19.RData")#removed exclude mice
#load(file="data/MLH1/MLH1_data_setup_11.12.19.RData")#added batch17
#load(file="data/MLH1/MLH1_data_setup_11.11.19.RData")#deleted DUP image
#load(file="data/MLH1/MLH1_data_setup_9.26.19.RData")#added batch16
#load(file="data/MLH1/MLH1_data_setup_8.29.19.RData") #
#load(file="data/MetaData.RData") #this was replacing most updated data file

### 2020-01-06 src/SetupData.Rmd
first try of incorporating batch18, still a few bugs

#todo :
#set the order to batches
#2 fileNames from batch 0 appear 2x, (1 is missing random name, the other has the same random name)

@@

MLH1_data <- MLH1_data[ ! MLH1_data$mouse %in% exclude_mice_list, ]

```{r adj_nMLH1, echo=FALSE}

#add a column with male adjusted MLH1 values (+1 to all males)
MLH1_data$adj_nMLH1.foci <- ifelse(MLH1_data$sex=="male", MLH1_data$nMLH1.foci+1, MLH1_data$nMLH1.foci)
MLH1_data$adj_nMLH1.foci <- as.numeric(MLH1_data$adj_nMLH1.foci)
```

@@

#order the batches in MLH1 and original

@@

batch.stats <- merge(original_batches,final_batches, by="BatchNum")## mm is the table of batch stats

@@

@@

@@

```{r Age.Hists, echo=FALSE, warning=FALSE, eval=FALSE}
#age.weeks col is missing

male_mouse_table_w.Ages <- AP_mouse_table.HQ[(AP_mouse_table.HQ$sex == "male") &(mouse.table_w.Ages$category != "other"),]

all.ages_plot <- ggplot(AP_mouse_table.HQ, aes(age.weeks))+geom_histogram(binwidth = 3)+facet_wrap(~category)+ggtitle("Male Age Distributions")
all.ages_plot

@@

save.image("~./MLH1repo/data/MLH1/MLH1_data_setup_12.20.19.RData")

>>>>

@@

MLH1_data <- MLH1_data[ ! MLH1_data$mouse %in% exclude_mice_list, ]
```

```{r adj_nMLH1, echo=FALSE}
#add a column with male adjusted MLH1 values (+1 to all males)
MLH1_data$adj_nMLH1.foci <- ifelse(MLH1_data$sex=="male", MLH1_data$nMLH1.foci+1, MLH1_data$nMLH1.foci)
MLH1_data$adj_nMLH1.foci <- as.numeric(MLH1_data$adj_nMLH1.foci)
```

@@

#order the batches in MLH1 and original
```

@@

batch.stats <- merge(original_batches,final_batches, by="BatchNum")## mm is the table of batch stats
##batch18 has the wrong number, ~390
```

@@

#remove the NAs
AP_mouse_table_w.Ages <- AP_mouse_table_w.Ages[!(is.na(AP_mouse_table_w.Ages$category.x) | AP_mouse_table_w.Ages$category.x==""), ]
```

@@

update the dissection document (that makes the meta.data DF)

@@

```{r Age.Hists, echo=FALSE, warning=FALSE}
#age.weeks col is missing

male_mouse_table_w.Ages <- AP_mouse_table_w.Ages[(AP_mouse_table_w.Ages$sex.x == "male") &(AP_mouse_table_w.Ages$category.x != "other"),]

all.ages_plot <- ggplot(AP_mouse_table_w.Ages[AP_mouse_table_w.Ages$sex.x == "male",], aes(age.weeks))+geom_histogram(binwidth = 3)+facet_wrap(~category.x)+ggtitle("Male Age Distributions")
all.ages_plot

@@

save.image("~./MLH1repo/data/MLH1/MLH1_data_setup_1.5.20.RData")
